---
title: "Paper: Solidarity and Performance Voting'"
author:
 - Heike Klüver, Humboldt
 - Felix Hartmann, Humboldt
 - Macartan Humphreys, WZB and Columbia
 - Ferdinand Geißler, Humboldt
 - Johannes Giesecke, Humboldt
date: "May 2021"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
    toc_depth: 2
    self_contained: yes
    code_folding: hide
  pdf_document:
    toc: yes
  word_document:
    toc: yes
    toc_depth: '2'
keywords: vaccine hesitancy, covid, transaction costs
theme: null
abstract: "Respondents support high levels of cash and vaccine transfers to help poorer nations. They are more supportive when health and economic risks of failing to provide support are high; but for the most part support does not depend on these calculations. Preferences over German policy are largely independent of what other countries are doing. Median support for vaccines (90 million) and cash (2 billion) corresponds closely to actual  (100 million doses and 2.2 billion cash)."
bibliography: references.bib  
editor_options:
  chunk_output_type: console
---


# Setup

```{r setup, echo=TRUE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE, comment=NA)
options(qwraps2_markup = "markdown")

## Packages
if (!require(pacman)) install.packages("pacman")

pacman::p_load(
  ggpubr,      # for ggarrange
  ggridges,    # plot
  cregg,       # conjoint
  readxl,      # read excel
  gtrendsR,    # google trends
  aod,         # hypothesis testing (1.3.1)
  car,         # linear hypothesis testing for causal tree (3.0-2)
  corrplot,    # Correlations (0.84)
  DeclareDesign, 
  dplyr,       # Data manipulation (0.8.0.1)
  evtree,      # evolutionary learning of globally optimal trees (1.0-7)
  fastDummies,
  fBasics,     # Summary statistics (3042.89)
  ggplot2,
  grf,         # Generalized random forests (0.10.2)
  haven,       # load sav
  kableExtra,  # Prettier RMarkdown (1.0.1)
  knitr,
  labelled,
  psych,       # Correlation p-values (1.8.12)
  purrr,
  rpart,       # Classification and regression trees, or CART (4.1-13)
  reshape2,
  rpart.plot,  # Plotting trees (3.0.6)
  readr,       # Reading csv files (1.3.1)
  sjlabelled,
  stats,
  summarytools,
  texreg,
  tidyverse,
  tidyselect,
  tidyr,       # Database operations (0.8.3)
  treeClust,   # Predicting leaf position for causal trees (1.1-7)
  tibble)      # Modern alternative to data frames (2.1.1)


# Set seed for reproducibility
set.seed(201911) 

```


```{r}

deal_labels = c("No deal"=0, "20 give 20 bn"=1, "40 give 20b"=2,
                "20 give 40 bn"=3, "40 give 40 bn"=4)

# c('Control: kein Abkommen'=0,
#   'Treatment: Abkommen, 20 Länder, 20 Milliarden'=1,
#   'Treatment: Abkommen, 40 Länder, 20 Milliarden'=2,
#   'Treatment: Abkommen, 20 Länder, 40 Milliarden'=3,
#   'Treatment: Abkommen, 40 Länder, 40 Milliarden'=4)

main_df <- read_csv('1_input/combined.csv')

w4 <- main_df %>% dplyr::filter(wave==4)

# labs <- var_label(w4) %>% unlist
# data.frame(names(labs), labs) %>% kable()

# creating vignettes

vign_values <- 
  expand.grid(trading_importance = 0:1, risk=0:1, deal=0:4) %>% 
  arrange(trading_importance, risk) %>% 
  set_value_labels(
    trading_importance = 
      c('Control: Wirtschaft bleibt unberührt'=0,
        'Treatment: Wirtschaft schrumpft um 5%'=1),
    risk=c('Control: Kein Risiko durch Mutationen'=0,
           'Treatment: Erhöhtes Risiko durch Mutationen'=1),
                   deal= deal_labels) %>%
  mutate(vignr=1:20) %>% as_tibble()

df <- 
  list(
    w4 %>%
      mutate(vignr = as.numeric(run1_exp8)) %>% left_join(vign_values) %>%
      mutate(round = 1,
         cash = 	exp7_money1,
         doses = exp7_doses1) %>%
      select(group, round, cash, doses, trading_importance, risk, deal, ID, perspective_fed_indian, perspective_fed_german, vaccinated),
    
    w4 %>%
      mutate(vignr = as.numeric(run2_exp8)) %>% left_join(vign_values) %>%
      mutate(round = 2,
         cash = 	exp7_money2,
         doses =  exp7_doses2) %>%
      select(group, round, cash, doses, trading_importance, risk, deal, ID, perspective_fed_indian, perspective_fed_german, vaccinated)) %>% 
  bind_rows %>%
  dplyr::filter(group !=3) %>% 
  mutate(id = ID,
         others_number = (deal==1 | deal == 3)*2 + (deal==2 | deal == 4)*4,
         others_giving = (deal==1 | deal == 2)*2 + (deal==3 | deal == 4)*4,
         others_average = others_giving/others_number, 
         others_average = ifelse(others_number==0, 0, others_average), 
         deal = factor(deal, deal_labels, names(deal_labels)),
         risk_factor = factor(risk, 0:1, c("Low", "High")),
         trading_factor = factor(trading_importance, 0:1, c("Low", "High")),
         risk = risk - mean(risk),
         trading_importance = trading_importance - mean(trading_importance),
         others_number_norm = others_number - mean(others_number),
         others_giving_norm = others_giving - mean(others_giving),
         cash_billions = 	cash*1000,
         cash_billions_log = 	log(1 + cash_billions))
```

# Raw patterns

## Coarsened histograms

```{r}
cash_histogram <- 
  df %>% mutate(coarsened_cash = ifelse(cash_billions > 12, 12, cash_billions)) %>% ggplot(aes(coarsened_cash)) + geom_histogram() + 
  xlab("Cash (censored at 12 billion") 

cash_histogram  

# Support sizes

amounts <- seq(0, 22, .5)

support <- function(df)
  data.frame(
    amounts = seq(0, 22, .5),
    support = sapply(amounts, function(j) 
      mean(df$cash_billions >= j, na.rm = TRUE)))

s1 <- list(
  Low = support(
    df %>% dplyr::filter(risk_factor == "Low" & trading_factor == "Low")),
  High  =  support(
    df %>% dplyr::filter(risk_factor == "High" & trading_factor == "High"))) %>% 
  bind_rows(.id = "Costs")

s2 <- list(
  Low = support(
    df %>% dplyr::filter(deal == "No deal")),
  High  =  support(
    df %>% dplyr::filter(deal == "40 give 40 bn"))) %>% 
  bind_rows(.id = "Mulilateralism")

supports <- ggarrange(
s1 %>% ggplot(aes(amounts, support, color = Costs)) + geom_line() + ylim(0,1) + theme_bw() + xlab("German contribution (bn)") + ylab("Share supporting")  + theme(legend.position="bottom"),
s2 %>% ggplot(aes(amounts, support, color = Mulilateralism)) + geom_line() + ylim(0,1) + theme_bw() + xlab("German contribution (bn)") + ylab("Share supporting")   + theme(legend.position="bottom"), nrow = 2)

pdf("2_output/cumulative.pdf", height = 8, width = 8)
 supports 
dev.off()

supports

```

```{r}
raw  <- 
  df %>% 
  mutate(costs = ((risk_factor == "High") + 2*(trading_factor=="High"))) %>%
  group_by(trading_factor, risk, deal, costs) %>% 
  summarize(cash_bn = median(cash_billions, na.rm = TRUE),
            doses = median(doses, na.rm = TRUE))  %>%
  gather("outcome","value",  -risk,  -deal, -trading_factor, -costs)

medians_plot <- 
raw %>% ggplot(aes(risk, value, color = trading_factor)) + 
  facet_grid(outcome ~ deal, scales = "free_y") + geom_point()  + geom_line() + ylim(c(0, NA)) + theme_bw() + ylab(" ")+
  scale_x_continuous(breaks=c(-.45,.45), labels = c("Low", "High")) 

pdf("2_output/medians.pdf", height = 5, width = 8)
 medians_plot 
dev.off()
# Note: use bootstrapping to add standard errors on the median?



observation_plot <- function(data = df)
data %>% dplyr::select(risk_factor, deal, trading_factor, cash_billions, doses, vaccinated) %>%
  mutate(cash_billions = ifelse(cash_billions>20, 20, cash_billions)) %>%
  gather("outcome","value",  -risk_factor,  -deal, -trading_factor, - vaccinated) %>%
  mutate(outcome = factor(outcome, c("cash_billions", "doses"), c("Billion Euros", "Million doses"))) %>% 
  ggplot(aes(risk_factor, value, color = trading_factor)) + facet_grid(outcome ~ deal, scales = "free_y") + geom_boxplot() + ylim(c(0, NA)) + theme_bw() + 
  scale_y_continuous(trans='sqrt') + ylab(" ") + xlab("Mutation risk") 


observation_plot()
```


Basic variation by vaccination status

```{r}

df %>% group_by(vaccinated) %>% 
  summarize(median_cash = median(cash_billions),
            mean_cash = mean(cash_billions),
            median_doses = median(doses),
            mean_doses = mean(doses),
            )
```

```{r}
main_results <- 
  list(
  cash = lm_robust(cash ~ trading_importance*risk*others_number_norm*others_giving_norm  + round, fixed_effects = ~id,  se_type = "stata", data = df) %>% tidy,
  doses = lm_robust(doses ~ trading_importance*risk*others_number_norm*others_giving_norm  + round, fixed_effects = ~id,  se_type = "stata", data = df) %>% tidy) %>% bind_rows()


 treatments <- c("trading_importance", "risk", "others_number", "others_giving")
 treatments_norm <- c("trading_importance", "risk", "others_number_norm", "others_giving_norm")

 treatment_labels <- c("Trading importance", "Risk", "Number of others giving (10s)", "Amount given by others\n(10s of billions)")
```

# Descriptives

The average proposal is: 
`r round(mean(df$cash, na.rm = TRUE), 2)` billion Euros and 
`r round(mean(df$doses, na.rm = TRUE), 2)` million doses. 

The median proposal is: 
`r round(median(df$cash_billions, na.rm = TRUE), 2)` billion Euros and 
`r round(median(df$doses, na.rm = TRUE), 2)` million doses. 
 
These are close to actual [https://www.auswaertiges-amt.de/en/aussenpolitik/themen/gesundheit/covax/2396914](pledges).


The median in risk conditions is proposal is: 
`r df %>% dplyr::filter(risk_factor=="High" & trading_factor == "High") %>% pull(cash_billions) %>% median(na.rm = TRUE) %>% round(2)` billion Euros and 
`r df %>% dplyr::filter(risk_factor=="High" & trading_factor == "High") %>% pull(doses) %>% median(na.rm = TRUE) %>% round(2)` million doses. 

```{r, out.width = "50%"} 
figure_1 <-
  
  main_results %>% 
  dplyr::filter(term %in% treatments_norm) %>% 
  mutate(Treatment = factor(term, treatments_norm, treatment_labels)) %>%
  
  ggplot(aes(estimate, Treatment)) + geom_point()+
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = .1)+
  geom_vline(xintercept=0, linetype="longdash", lwd=0.35, colour = "#B55555") + 
  theme_bw() + facet_grid(~outcome, scales = "free_x")+
  ylab("")


df_mean <- df %>% 
  group_by(risk_factor) %>% 
  summarize(average = mean(cash_billions, na.rm = TRUE)) %>%
  ungroup() 

figure_2 <-
  df %>% 
  ggplot(aes(risk_factor, cash_billions)) + 
  geom_boxplot() + ylab("Billions of Euros")   + xlab("Risk")  + scale_y_sqrt() +
  geom_point(data = df_mean,
             mapping = aes(x = risk_factor, y = average),
             color="red") 

figure_3 <-
  df %>% 
  ggplot(aes(risk_factor, doses)) + 
  geom_boxplot() + ylab("Millions of doses") + xlab("Risk")

figure_2
figure_3
```

Note that the doses options was limited to between 0 and 200 m. 


Offers are responsive to risk and economic impacts but not much to coordination considerations.

```{r}

figure_1

pdf("2_output/E1_main.pdf", width = 6, height = 4)
figure_1
dev.off()
```


Trading importance and risk are substitutes for cash but not doses.

Without demeaning:

```{r}
lm_robust(cash_billions ~ trading_factor*risk_factor+ round, fixed_effects = ~id,  se_type = "stata", data = df) %>% tidy  %>% 
  kbl(digit =2) %>%
  kable_minimal()
```

Logging helps and substitution not as strong:

```{r}
lm_robust(log(cash_billions+1) ~ trading_factor*risk_factor+ round, fixed_effects = ~id,  se_type = "stata", data = df) %>% tidy  %>% 
  kbl(digit =2) %>%
  kable_minimal()

```

## Full results from saturated models

```{r}
main_results %>% 
  kbl(digit =2) %>%
  kable_minimal()
```


## Experiment

```{r}
outcomes <- c("solidarity_behaviour", "solidarity_attitude")
outcome_labels <- c("Solidarity Bahaviour", "Solidarity Attitude")
w2_treatments <- c("treatment_video")
w2_treatment_labels <- c("Treatment")
```


```{r, results = "asis"}
#r, child = "2_main_results.Rmd", eval = TRUE}
# put in separate files later

df_2 <- dplyr::filter(main_df, wave == 2)


# df_2$solidarity_bahaviour %>% 
#  hist(main = "Distribution of allocations from behavioral measure")



df_2 %>%
  ggplot(aes(factor(party_id), solidarity_behaviour)) + geom_boxplot()
  
  ggtitle("Distribution of allocations from behavioral measure")

stargazer::stargazer(
  lm(solidarity_behaviour ~ treatment_video, data = df_2), 
  lm(solidarity_attitude ~ treatment_video, data = df_2), 
  header = FALSE, type = "latex")

models_basic <- lapply(c(outcomes), function(y)
lm_robust(as.formula(paste(y, "~",   paste(w2_treatments, collapse =  "+"))), data = df_2))
names(models_basic) <- outcomes


figure_video <- 
  lapply(models_basic, tidy) %>% bind_rows(.id = "outcome") %>%
  dplyr::filter(term != "(Intercept)") %>%
  mutate(outcome = factor(outcome, outcomes, outcome_labels)) %>% 
  ggplot(aes(estimate, outcome)) + geom_point() +
  #facet_grid(~outcome) +
  geom_pointrange(aes(xmin = conf.low, xmax = conf.high), position = position_dodge(width = 0.3), width = .1)+
  theme_bw()+
  #ylab("Change in support for regime (0-1)") +
    geom_vline(xintercept=0, linetype="longdash", lwd=0.35, size=0.75,alpha=0.3, colour = "#B55555")  +
    xlab("") + ylab("")  +
    theme(#panel.grid.major = element_blank(),
          #panel.grid.minor = element_blank(),
          #panel.background = element_blank(),
          #strip.background = element_blank(),
          # strip.text.y = element_blank(),
          #axis.text.y=element_blank(),
          legend.position = "top",
          text = element_text(size=20),
          legend.title=element_blank(),
          strip.text.y = element_text(angle = 180),
          axis.ticks.y=element_blank()) +
    scale_color_grey()


figure_video

```

## Longer term follow up


```{r}

table(df$ID %in% df_2$ID)

df <- left_join(df, df_2 %>% dplyr::select(ID, treatment_video))

lm_robust(log(cash_billions+1) ~ trading_factor*risk_factor+ treatment_video + round,  se_type = "stata", data = df) %>% tidy  %>% 
  kbl(digit =2) %>%
  kable_minimal()

```


## Individual solidarity

Should an older Indian woman be prioritized over a young German?

```{r}

hist(df$perspective_fed_german - df$perspective_fed_indian)

lm_robust(log(cash_billions+1) ~ trading_factor*risk_factor+ treatment_video + round + perspective_fed_german +perspective_fed_indian,  se_type = "stata", data = df) %>% tidy  %>% 
  kbl(digit =2) %>%
  kable_minimal()

```


## Structural


```{r}
structural_results <- 
  lm_robust(cash_billions ~ trading_importance + risk + others_average, fixed_effects = ~id,  se_type = "stata", data = df) %>% tidy 

gamma <- structural_results$estimate[3] / (1- structural_results$estimate[3])
beta  <- 2*(1+gamma)*structural_results$estimate[1]
delta  <- 2*(1+gamma)*structural_results$estimate[2]

gamma_lwr <- structural_results$conf.low[3] / (1- structural_results$conf.low[3])
gamma_upr <- structural_results$conf.high[3] / (1- structural_results$conf.high[3])

b <- seq(structural_results$conf.low[3], structural_results$conf.high[3], length = 10)
b/(1-b)

pars <- c(gamma = gamma, beta = beta, delta = delta, gamma_lwr = gamma_lwr, gamma_upr = gamma_upr)
```


## Observational data

```{r}
owd <- read.csv("1_input/owid-covid-data.csv")

 small_owd <- owd %>% 
   dplyr::filter(date == "2021-10-20" & continent != "") %>% 
   select(iso_code, location, gdp_per_capita, population, people_fully_vaccinated_per_hundred, total_deaths_per_million, total_vaccinations) %>% 
   left_join(
     owd %>% dplyr::filter(date == "2021-04-05" & continent != "") %>%
       select(iso_code, location, total_deaths_per_million) %>%
       rename(historical_deaths_per_million = total_deaths_per_million))
 
 small_owd$total_vaccinations %>% sum(na.rm = TRUE)
 
 table(small_owd$people_fully_vaccinated_per_hundred %>% is.na)
 
r2_gdp <- lm_robust(
  people_fully_vaccinated_per_hundred ~  gdp_per_capita,
  data = small_owd)$r.squared

r2_deaths_1 <- lm_robust(
  people_fully_vaccinated_per_hundred ~  total_deaths_per_million,
  data = small_owd)$r.squared

r2_deaths_0 <- lm_robust(
  people_fully_vaccinated_per_hundred ~  historical_deaths_per_million,
  data = small_owd)$r.squared

c(r2_gdp, r2_deaths_1, r2_deaths_0)

80000000000/ small_owd %>% dplyr::filter(gdp_per_capita > 27000) %>% pull(population) %>% sum

pc <- 80000000000/ small_owd %>% dplyr::filter(gdp_per_capita > 27000) %>% pull(population) %>% sum

small_owd <- small_owd %>% mutate(
  bill = ifelse(gdp_per_capita > 27000, pc*population, 0)
)

small_owd %>% dplyr::filter(location == "Germany" | location == "United States" )
```


## Wave 2 conjoint


```{r, results = "asis"}

label <- "1_input/W2_exp3_vignettes_universe.dta" %>% 
  read_dta() %>%  
    mutate(vignr = as.numeric(vignr))


label$vig_doses %>% table()


conjoints <- 
  
  list(
    conjoint1_1 =
      df_2 %>%
      mutate(vignr = as.numeric(c_0031_w2),
             outcome = conjoint_choice1_exp3, rating = conjoint_rating1_exp3, contest = 1, candidate=1) %>%
      select(ID, vignr, outcome, rating, contest, candidate),
    
  conjoint1_2 =
      df_2 %>%
      mutate(vignr = as.numeric(c_0032_w2),
             outcome = conjoint_choice1_exp3, rating = conjoint_rating2_exp3, contest = 1, candidate=2) %>%
      select(ID, vignr, outcome, rating, contest, candidate), 

    
  conjoint2_1 =
      df_2 %>%
      mutate(vignr = as.numeric(vignette3),
             outcome = conjoint_choice2_exp3, rating = conjoint_rating3_exp3, contest = 2, candidate=1) %>%
      select(ID, vignr, outcome, rating, contest, candidate), 

        
    conjoint2_2 =
      df_2 %>%
      mutate(vignr = as.numeric(vignette4),
             outcome = conjoint_choice2_exp3, rating = conjoint_rating4_exp3, contest = 2, candidate=2) %>%
      select(ID, vignr, outcome, rating, contest, candidate), 

            
                conjoint3_1 =
      df_2 %>%
      mutate(vignr = as.numeric(vignette5),
             outcome = conjoint_choice3_exp3, rating = conjoint_rating5_exp3, contest = 3, candidate=1) %>%
      select(ID, vignr, outcome, rating, contest, candidate), 

                
                    conjoint3_2 =
      df_2 %>%
      mutate(vignr = as.numeric(vignette6),
             outcome = conjoint_choice3_exp3, 
             rating = conjoint_rating6_exp3, contest = 3, candidate=2) %>%
      select(ID, vignr, outcome, rating, contest, candidate) 
                    
) %>% bind_rows() %>%
  mutate(outcome = ifelse(candidate ==1, as.numeric(outcome=="1"), as.numeric(outcome=="2"))) %>%
  left_join(label) %>%
  mutate(
    doses = factor(
      vig_doses, 0:3,
      c("1 Million doses", "5 Million doses", "10 Million doses", "20 Million doses")),
    share = factor(vig_dose_share, 0:3,
      c("1 % of the vaccines", "5 % of the vaccines", "10 % of the vaccines", "20 % of the vaccines")),
    number= factor(vig_countries, 0:2, c("20 countries", "80 countries", "160 countries")), 
    economic_benefits= factor(vig_benefit_economic, 0:1, c("Without economic importance", "With economic importance")),
    health_benefits=factor(vig_benefit_health, 0:1,  
      c("No risk of infection", "Risk of infection"))) %>%
  left_join(df_2 %>% dplyr::select(ID, treatment_video)) 

# Normalizae data
# Note that mean rating is removed
conjoints_norm <- conjoints %>% 
  mutate(doses_norm = vig_doses - mean(vig_doses),
         number_norm = vig_countries - mean(vig_countries),
         share_norm = vig_dose_share - mean(vig_dose_share),
         economic_benefits = vig_benefit_economic - mean(vig_benefit_economic),
         health_benefits = vig_benefit_health - mean(vig_benefit_health)) %>%
  group_by(ID) %>% mutate(rating = rating - mean(rating)) %>% ungroup %>%
  left_join(df_2 %>% dplyr::select(ID, treatment_video))


models_interactions <-
  list(
    rating0 = lm_robust(rating ~  doses_norm*share_norm*number_norm*economic_benefits*health_benefits, data = conjoints_norm),
    rating1 = lm_robust(rating ~  doses_norm*share_norm*number_norm*economic_benefits*health_benefits, data = conjoints_norm),
    choice0 = lm_robust(outcome ~  doses_norm*share_norm*number_norm*economic_benefits*health_benefits, data = conjoints_norm),
    choice1 = lm_robust(outcome ~  doses_norm*share_norm*number_norm*economic_benefits*health_benefits, data = conjoints_norm)
  )


models_treatments <-
  list(
    rating = lm_robust(rating ~  treatment_video*vig_doses + treatment_video*vig_dose_share + treatment_video*vig_countries + treatment_video*vig_benefit_economic + treatment_video*vig_benefit_health, 
                        data = conjoints_norm),
    choice = lm_robust(outcome ~  treatment_video*vig_doses + treatment_video*vig_dose_share + treatment_video*vig_countries + treatment_video*vig_benefit_economic + treatment_video*vig_benefit_health, 
                        data = conjoints_norm)
    )

htmlreg(models_interactions)

htmlreg(models_treatments)

fileConn <- file("2_output/treatment_effects.tex")
writeLines(texreg(models_treatments, float.pos = "h!", include.ci = FALSE, caption = "Effects of treatment on drivers of support for agreements. ",
  custom.coef.map = list(
    "(Intercept)" = "Constant (Average rating)",
    "treatment_video" = "Video effect (given ungenerous agreement)",
    "vig_doses" = "German contribution",
    "vig_dose_share" = "German share",
"vig_countries" = "Number of donors",
"vig_benefit_economic" = "Economic benefits",
"vig_benefit_health" = "Health benefits",
"treatment_video:vig_doses" = "Video * Contribution",
"treatment_video:vig_dose_share" = "Video * Share",
"treatment_video:vig_countries" = "Video * Donors",
"treatment_video:vig_benefit_economic" = "Video * Economics",
"treatment_video:vig_benefit_health"= "Video * Health"
    ), digits = 3), fileConn)
close(fileConn)


      
```

## amce

```{r}
amces <- 
  conjoints %>% 
  cj(rating ~ doses+share+number+ economic_benefits+health_benefits,
            id =~ID)

pdf("2_output/amces.pdf", width = 5, height = 4)
 plot(amces) + theme(legend.position="none")
dev.off()
```


## Notes

These seem inconsistent but they really tap into different questions; they suggest preferences for small doses and suggest preferences that are not ver responsive to other conditions.  

Number of states blows everything else out of the water. This is really about what types of deals does Germany want: Germans want deals to be multilateral with sharing. 

Also the benefits conditions are conceptually muddled with numbers conditions.
Note:

* Regressions take numbers at face value despite uneven gaps
* The economic result is  weird, is it possible there's backwards coding.



## Save workspace

```{r}
save.image("Solidarity.Rdata")
```


```{r}
owd <- read.csv("1_input/owid-covid-data.csv")  %>% 
   dplyr::filter(date == "2021-10-20" & continent != "")

DAC_countries <- c("Australia",  "Austria",  "Belgium",  "Canada", "Czechia",  "Denmark", "Finland",  "France", "Germany",  "Greece", "Hungary",  "Iceland", "Ireland", "Italy", "Japan",  "South Korea", "Luxembourg", "Netherlands",  "New Zealand", "Norway", "Poland", "Portugal", "Slovakia", "Slovenia", "Spain", "Sweden", "Switzerland", "United Kingdom", "United States")

owd <- owd %>% 
  mutate(DAC = location %in%  DAC_countries,
         share = ifelse(DAC, gdp_per_capita * population, 0),
         share = share/sum(share),
         amount = 63*share)

owd %>% dplyr::filter(DAC) %>% select(location, share, amount) %>% kable()

```
