---
title: "Paper: Vaccine Solidarity"
author:
 - Heike Klüver, Humboldt
 - Felix Hartmann, Humboldt
 - Macartan Humphreys, WZB and Columbia
 - Ferdinand Geißler, Humboldt
 - Johannes Giesecke, Humboldt
date: "May 2021"
output:
  pdf_document:
    number_sections: true
keywords: vaccine hesitancy, covid, transaction costs
theme: null
abstract: "Respondents support high levels of cash and vaccine transfers to help poorer nations. They are more supportive when health and economic risks of failing to provide support are high; but for the most part support does not depend on these calculations. Preferences over German policy are largely independent of what other countries are doing. Median support for vaccines (90 million) and cash (2 billion) corresponds closely to actual  (100 million doses and 2.2 billion cash)."
bibliography: references.bib  
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(kableExtra)
library(DeclareDesign)
load("Solidarity.Rdata")
```

# Introduction


# Design

# Results

## Main results

Experimental results on agreements

```{r, echo = FALSE}
figure_1
```

* Note complementarity in giving
* Invariance to numbers of other countries: discuss


## Nudges on solidarity

### Individual solidarity measure

* Attitudinal
* Behavioral
* Should an older Indian woman be prioritized over a young German?

```{r, echo = FALSE}
hist(df$solid_indian_bund - df$solid_german_bund, main = "Older Indian Woman prioritized", xlab = "Relative vaccination prioritziation")
```

### Video treatment

```{r}
figure_video
```


### Longer term effects on solidarity.

```{r, echo = FALSE}
lm_robust(solid_indian_bund ~ treatment_video,  se_type = "stata", data = df) %>% tidy  %>% 
  kbl(digit =2, booktabs = TRUE)

```

## Interpretation

Solidarity on giving

```{r, echo = FALSE}
lm_robust(log(cash+1) ~ solid_german_bund +solid_indian_bund,  se_type = "stata", data = df) %>% tidy  %>% 
  kbl(digit =2, booktabs = TRUE)
```

Longer term effects on giving

```{r, echo = FALSE}
lm_robust(log(cash+1) ~ trading_factor*risk_factor+ treatment_video + round + solid_german_bund +solid_indian_bund,  se_type = "stata", data = df) %>% tidy  %>% 
  kbl(digit =2, booktabs = TRUE)
```


### Structural analysis

In our pre-analysis plan we stipulated a model in which citizens place a value on own contributions $x_i$, given contributions by others $n \overline{x}_{-i}$. Their utility reflects gains from total contributions, which reflect both altruism and risks,  costs of own contributions. and costs of deviation from a norm of giving in line with contributions by others.

We begin with a simplification in which utility is given by:

$$u_i = (\alpha + \beta Z_1 + \delta Z_2) \left(n_{-i}\overline{x}_{-i} + x_i\right) - x_i^2 - \gamma(x_i-\overline{x}_{-i})^2$$

<!-- Then first order conditions are:  -->

<!-- $$(\alpha_i + \beta Z_1 + \delta Z_2)  - 2x_i - 2\gamma(x_i-\overline{x}_{-i})=0$$ -->
<!-- <!-- $$(\alpha_i + \beta_i Z_1 + \delta Z_2)/2 +\gamma \delta\overline{x}_{-i} = x_i(1+\gamma)$$ --> -->

Optimal contributions are then given by:

$$x_i^* = \frac{\alpha_i}{1+\gamma} + \frac{\beta}{2+2\gamma} Z_1 + \frac{\delta}{2+2\gamma}Z_2 +\frac{\gamma}{1+\gamma}\overline{x}_{-i}$$

The parameters here can be estimated with ordinary least squares. 

```{r, include = FALSE}
structural_results %>% kable()
```

```{r, echo = FALSE}
data.frame(parameter = names(pars), value = pars) %>%   kbl(digit =2, booktabs = TRUE)

```


To do: extend. \footnote{The model in the pre-analysis plan has utility:

$$(\alpha_i + \beta_i Z_1 + \delta Z_2) \log\left(\sum_j x_j\right) - x_i^2 - \gamma(x_i-\kappa\overline{x}_{-i})^2$$

which in turn implies optimal contributions given by:

% $$(\alpha_i + \beta_i Z_1 + \delta Z_2) \log\left(n_{-i}\overline{x}_{-i} + x_i\right) - x_i^2 - \gamma(x_i-\kappa\overline{x}_{-i})^2$$

% First order conditions are:

% $$\frac{\alpha_i + \beta_i Z_1 + \delta Z_2}{n_{-i}\overline{x}_{-i} + x_i} - 2x_i - 2\gamma(x_i-\kappa\overline{x}_{-i}) = 0$$
% $$\frac{\alpha_i + \beta_i Z_1 + \delta Z_2}{n_{-i}\overline{x}_{-i} + x_i} = 2x_i + 2\gamma(x_i-\kappa\overline{x}_{-i})$$
% $$2x_i(1+\gamma)(n_{-i}\overline{x}_{-i} + x_i) - 2\gamma(\kappa\overline{x}_{-i})(n_{-i}\overline{x}_{-i} + x_i) - \alpha_i - \beta_i Z_1 - \delta Z_2 = 0$$
% $$2(1+\gamma)x_i^2 + 2x_i((1+\gamma)(n_{-i}\overline{x}_{-i})-\gamma(\kappa\overline{x}_{-i})) - 2\gamma\kappa n_{-i}\overline{x}_{-i}^2 - \alpha_i - \beta_i Z_1 - \delta Z_2 = 0$$

% $$2(1+\gamma)x_i^2 + 2x_i(n_{-i} +\gamma(n_{-i}-\kappa))\overline{x}_{-i} - 2\gamma\kappa n_{-i}\overline{x}_{-i}^2 - \alpha_i - \beta_i Z_1 - \delta Z_2 = 0$$
% $$(1+\gamma)x_i^2 + x_i(n_{-i} +\gamma(n_{-i}-\kappa))\overline{x}_{-i} - (\gamma\kappa n_{-i}\overline{x}_{-i}^2 +(\alpha_i + \beta_i Z_1 + \delta Z_2)/2) = 0$$

% With solution:

$$x_i^* = \frac{-(n_{-i} +\gamma(n_{-i}-\kappa))\overline{x}_{-i}+\sqrt{((n_{-i} +\gamma(n_{-i}-\kappa))\overline{x}_{-i})^2 + 4(1+\gamma)(\gamma\kappa n_{-i}\overline{x}_{-i}^2 +(\alpha_i + \beta_i Z_1 + \delta Z_2)/2)}}{2(1+\gamma)}$$ We see again that $\gamma$ appears in the denominator. }


# Discussion


Risk: YES
Peer effects: SOMEWHAT
Base solidarity: YES
