---
title: "Paper: Solidarity"
author:
 - Ferdinand Geißler, Humboldt
 - Felix Hartmann, Humboldt
 - Macartan Humphreys, WZB and Columbia University
 - Heike Klüver, Humboldt
 - Johannes Giesecke, Humboldt
date: "January 2022"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
    toc_depth: 2
    self_contained: yes
    code_folding: hide
  pdf_document:
    toc: yes
  word_document:
    toc: yes
    toc_depth: '2'
keywords: vaccine solidarity
# theme: null
editor_options:
  chunk_output_type: console
---


# Setup

```{r setup, echo=TRUE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE, comment=NA)
# options(qwraps2_markup = "markdown")

## Packages
if (!require(pacman)) install.packages("pacman")

pacman::p_load(
  ggpubr,      # for ggarrange
  cregg,       # conjoint
  estimatr, 
  haven,       # load sav
  kableExtra,  # Prettier RMarkdown (1.0.1)
  knitr,
  labelled,
  sjlabelled,
  stargazer,
  texreg,
  tidyverse
)  

# Whether to run from raw data
prep_data <- FALSE
```

# Data preparation

```{r}

deal_labels <- c("No deal" =0, 
                 "20 give 20 bn" = 1, 
                 "40 give 20b" = 2,
                 "20 give 40 bn" = 3, 
                 "40 give 40 bn" = 4)

# vignettes values

vign_values <- 
  expand.grid(trading_importance = 0:1, risk=0:1, deal=0:4) %>% 
  arrange(trading_importance, risk) %>% 
  set_value_labels(
    trading_importance = 
      c('Control: Wirtschaft bleibt unberührt'=0,
        'Treatment: Wirtschaft schrumpft um 5%'=1),
    risk=c('Control: Kein Risiko durch Mutationen'=0,
           'Treatment: Erhöhtes Risiko durch Mutationen'=1),
    deal= deal_labels) %>%
  mutate(vignr=1:20) %>% 
  as_tibble()


head(vign_values) |> 
  kable(caption = "Conditions", format = "pipe")

```


```{r}

if(prep_data){
  
main_df <- read_csv('1_input/combined.csv') %>% 
  mutate(
    party = factor(party_id, 1:9, 
                   c("CDU.CSU", "CDU.CSU", 
                     "SPD", "AFD", "Greens", 
                     "FDP", "Left", "Other", 
                     "No party"))) %>%
  group_by(ID) %>% 
  mutate(migration_background = mean(migration_background, na.rm = TRUE)) %>%
  ungroup()

df_2 <- dplyr::filter(main_df, wave == 2) |>
  select(ID, solidarity_behaviour, solidarity_attitude, treatment_video, 
         starts_with("c_0031"), 
         starts_with("c_0032"),
         starts_with("vignette"),
         starts_with("conjoint_"))
         
w4 <- main_df |> 
  dplyr::filter(wave==4) |>
  select(group, ID, 
         perspective_fed_indian, perspective_fed_german,
         vaccinated, party, migration_background, 
         run1_exp8, exp7_money1, exp7_doses1, 
         run2_exp8, exp7_money2, exp7_doses2)

df_4 <- 
  
  list(
    
    w4 %>%
      mutate(vignr = as.numeric(run1_exp8), round = 1) |>
      rename(cash = 	exp7_money1, doses = exp7_doses1),
    
    w4 %>%
      mutate(vignr = as.numeric(run2_exp8), round = 2) |>
      rename(cash = 	exp7_money2, doses =  exp7_doses2)
    ) %>% 
  
  bind_rows %>%
  
  left_join(vign_values) %>%
  
  dplyr::filter(group !=3) %>% 
  
  mutate(id = ID,
         others_number = (deal==1 | deal == 3)*2 + (deal==2 | deal == 4)*4,
         others_giving = (deal==1 | deal == 2)*2 + (deal==3 | deal == 4)*4,
         others_average = others_giving/others_number, 
         others_average = ifelse(others_number==0, 0, others_average), 
         deal = factor(deal, deal_labels, names(deal_labels)),
         risk_factor = factor(risk, 0:1, c("Low", "High")),
         trading_factor = factor(trading_importance, 0:1, c("Low", "High")),
         risk = risk - mean(risk),
         trading_importance = trading_importance - mean(trading_importance),
         others_number_norm = others_number - mean(others_number),
         others_giving_norm = others_giving - mean(others_giving),
         cash_billions = 	cash*1000,
         cash_billions_log = 	log(1 + cash_billions)) |>
  left_join(df_2)



df_4  |> write_rds("df_4.rds")
df_2  |> write_rds("df_2.rds")


}

  df_4 <- read_rds("df_4.rds")
  df_2 <- read_rds("df_2.rds")

```

# Numbers provided in Introduction (Vaccine background data from OWID)

```{r}
owd <- read.csv("1_input/owid-covid-data-20221007.csv") 

owd_world <- filter(owd, location == "World")
  
owd <- owd  |>
     dplyr::filter(continent != "")

alt_date = "2022-10-01"
survey_date = "2021-09-22"

small_owd <- owd %>% 
   dplyr::filter(date == survey_date) %>% 
   select(iso_code, location, gdp_per_capita, population, people_fully_vaccinated_per_hundred, total_deaths_per_million, total_vaccinations) 

small_owd_alt <- owd %>% 
   dplyr::filter(date == alt_date) %>% 
   select(iso_code, location, gdp_per_capita, population, people_fully_vaccinated_per_hundred, total_deaths_per_million, total_vaccinations) 
```

## Global vaccination

```{r}
owd_world |> 
  filter(date %in% c(survey_date, alt_date)) |>
  select(date, people_fully_vaccinated_per_hundred, total_vaccinations) |> 
  kable(caption = "Vaccination at the time of survey and most recently", format = "pipe")

```


## Historical distribution as explained by GDP and by deaths

```{r}

r2s <- c(
  r2_gdp = lm_robust(
  people_fully_vaccinated_per_hundred ~  gdp_per_capita,
  data = small_owd)$r.squared,

  r2_deaths = lm_robust(
  people_fully_vaccinated_per_hundred ~  total_deaths_per_million,
  data = small_owd)$r.squared,
  
  r2_deaths_most_recent = lm_robust(
  people_fully_vaccinated_per_hundred ~  total_deaths_per_million,
  data = small_owd_alt)$r.squared)

data.frame(var = names(r2s), R2 = r2s)|> kable(format = "pipe")
```


## Coverage in top 10 and bottom 10 countries (with data and population > 500,000)

```{r}
small_owd |> 
  arrange(people_fully_vaccinated_per_hundred) |>
  filter(!is.na(people_fully_vaccinated_per_hundred) & 
           population > 500000) |> 
  mutate(N = n()) |>
  select(location, people_fully_vaccinated_per_hundred, N) |>
  slice(10, (n()-9)) %>%
  kable(caption = "Most and least vaccinated", format = "pipe")


small_owd_alt |> 
  arrange(people_fully_vaccinated_per_hundred) |>
  filter(!is.na(people_fully_vaccinated_per_hundred) & 
           population > 500000) |> 
  mutate(N = n()) |>
  select(location, people_fully_vaccinated_per_hundred, N) |>
  slice(10, (n()-9)) %>%
  kable(caption = "Most and least vaccinated, most recent---note few countries reporting", format = "pipe")
  
```

### Assessed shares 

```{r}

pc <- 80000000000/ (small_owd %>% dplyr::filter(gdp_per_capita > 27000) %>% pull(population) %>% sum)

small_owd <- small_owd %>% mutate(
  bill = ifelse(gdp_per_capita > 27000, pc*population, 0)
)

small_owd %>% 
  dplyr::filter(location == "Germany" | location == "United States" ) %>% 
  kable(format = "pipe")
```


# Analysis: Raw patterns


```{r}
# Support sizes

amounts_d <- seq(0, 22, .5)
amounts_v <- seq(0, 200, 1)

# Figures cumulative distribution
support <- function(x = df_4$cash_billions, amounts = amounts_d)
  data.frame(
    amounts = amounts,
    support = sapply(amounts, function(j) 
      mean(x >= j, na.rm = TRUE)))

s1 <- list(
  Low = support(
    df_4 %>% dplyr::filter(risk_factor == "Low" & trading_factor == "Low") %>% pull(cash_billions), 
    amounts = amounts_d),
  High  =  support(
    df_4 %>% dplyr::filter(risk_factor == "High" & trading_factor == "High")%>% pull(cash_billions), amounts = amounts_d)) %>% 
  bind_rows(.id = "Costs")

s2 <- list(
  Low = support(
    df_4 %>% dplyr::filter(deal == "No deal") %>% pull(cash_billions)),
  High  =  support(
    df_4 %>% dplyr::filter(deal == "40 give 40 bn") %>% pull(cash_billions))) %>% 
  bind_rows(.id = "Multilateralism")


s3 <- list(
  Low = support(
    df_4 %>% dplyr::filter(risk_factor == "Low" & trading_factor == "Low") %>% pull(doses), amounts_v),
  High  =  support(
    df_4 %>% dplyr::filter(risk_factor == "Low" & trading_factor == "High") %>% pull(doses), amounts_v)) %>% 
  bind_rows(.id = "Costs")

s4 <- list(
  Low = support(
    df_4 %>% dplyr::filter(deal == "No deal") %>% pull(doses), amounts_v),
  High  =  support(
    df_4 %>% dplyr::filter(deal == "40 give 40 bn") %>% pull(doses), amounts_v)) %>% 
  bind_rows(.id = "Multilateralism")

```


# Figure 1: Distribution of support for contributions of different sizes

```{r}
supports <-
  ggarrange(
    s1 %>% ggplot(aes(amounts, support, color = Costs)) + geom_line() + ylim(0, 1) + 
      theme_bw() + 
      xlab("German contribution (bn Euro)") + ylab("Share supporting")  + 
      theme(legend.position = "bottom"),
    
    s2 %>% ggplot(aes(amounts, support, color = Multilateralism)) + geom_line() + ylim(0, 1) + 
      theme_bw() + 
      xlab("German contribution (bn  Euro)") + 
      ylab("Share supporting")   + 
      theme(legend.position = "bottom") + ylab(""),
    
    s3 %>% ggplot(aes(amounts, support, color = Costs)) + geom_line() + ylim(0, 1) + theme_bw() + xlab("German contribution (mio vaccines)") + ylab("Share supporting")  + theme(legend.position = "bottom"),
    
    s4 %>% ggplot(aes(amounts, support, color = Multilateralism)) + geom_line() + ylim(0, 1) + theme_bw() + xlab("German contribution (mio vaccines)") + ylab("Share supporting")   + theme(legend.position =  "bottom") + ylab(""),
    
    nrow = 2,
    ncol = 2
  )

pdf("2_output/cumulative.pdf", height = 6, width = 10)
 supports 
dev.off()


supports

```



Basic variation by vaccination status

```{r}

df_4 %>% group_by(vaccinated) %>% 
  summarize(median_cash = median(cash_billions),
            mean_cash = mean(cash_billions),
            median_doses = median(doses),
            mean_doses = mean(doses),
            ) |>
  kable(format = "pipe")
```

```{r}
main_results <- 
  list(
  cash = lm_robust(cash_billions ~ trading_importance*risk*others_number_norm*others_giving_norm  + round, fixed_effects = ~id,  se_type = "stata", data = df_4) %>% tidy,
  doses = lm_robust(doses ~ trading_importance*risk*others_number_norm*others_giving_norm  + round, fixed_effects = ~id,  se_type = "stata", data = df_4) %>% tidy) %>% bind_rows()


 treatments <- c("trading_importance", "risk", "others_number", "others_giving")
 treatments_norm <- c("trading_importance", "risk", "others_number_norm", "others_giving_norm")

 treatment_labels <- c("Trading importance", "Risk", "Number of others giving (10s)", "Amount given by other countries\n(10s of billions)")
```


Basic variation by risk factor


```{r}
df_4 %>% group_by(risk_factor) %>% 
  summarize(
  median_cash = median(cash_billions),
  mean_cash = mean(cash_billions),  
  median_doses = median(doses),
  mean_doses = mean(doses)) |>
  kable(format = "pipe")

```


# Figure 2: Marginal effects of conditions


The average proposal is: 
`r round(mean(df_4$cash_billions, na.rm = TRUE), 2)` billion Euros and 
`r round(mean(df_4$doses, na.rm = TRUE), 2)` million doses. 

The median proposal is: 
`r round(median(df_4$cash_billions, na.rm = TRUE), 2)` billion Euros and 
`r round(median(df_4$doses, na.rm = TRUE), 2)` million doses. 
 
These are close to actual [https://www.auswaertiges-amt.de/en/aussenpolitik/themen/gesundheit/covax/2396914](pledges).


The median in risk conditions is proposal is: 
`r df_4 %>% dplyr::filter(risk_factor=="High" & trading_factor == "High") %>% pull(cash_billions) %>% median(na.rm = TRUE) %>% round(2)` billion Euros and 
`r df_4 %>% dplyr::filter(risk_factor=="High" & trading_factor == "High") %>% pull(doses) %>% median(na.rm = TRUE) %>% round(2)` million doses. 

```{r, out.width = "50%"} 
figure_2 <-
  
  main_results %>% 
  dplyr::filter(term %in% treatments_norm) %>% 
  mutate(Treatment = factor(term, treatments_norm, treatment_labels),
         outcome = factor(outcome, c("cash_billions", "doses"), c("Cash (billion Euros)", "Doses (Millions)"))) %>%
  
  ggplot(aes(estimate, Treatment)) + geom_point()+
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = .1)+
  geom_vline(xintercept=0, linetype="longdash", lwd=0.35, colour = "#B55555") + 
  theme_bw() + facet_grid(~outcome, scales = "free_x")+
  ylab("")


df_mean <- df_4 %>% 
  group_by(risk_factor) %>% 
  summarize(average = mean(cash_billions, na.rm = TRUE)) %>%
  ungroup() 

figure_2_1 <-
  df_4 %>% 
  ggplot(aes(risk_factor, cash_billions)) + 
  geom_boxplot() + ylab("Billions of Euros")   + xlab("Risk")  + scale_y_sqrt() +
  geom_point(data = df_mean,
             mapping = aes(x = risk_factor, y = average),
             color="red") 

figure_2_2 <-
  df_4 %>% 
  ggplot(aes(risk_factor, doses)) + 
  geom_boxplot() + ylab("Millions of doses") + xlab("Risk")

figure_2_1
figure_2_2
```


Note that the doses options was limited to between 0 and 200 m. 


Offers are responsive to risk and economic impacts but not much to coordination considerations.

```{r}

figure_2

pdf("2_output/E1_main.pdf", width = 6, height = 3)
figure_2
dev.off()
```

Trading importance and risk are substitutes for cash but not doses.

Without demeaning:

```{r}
lm_robust(cash_billions ~ trading_factor*risk_factor+ round, fixed_effects = ~id,  se_type = "stata", data = df_4) %>% tidy  %>% 
  kbl(digit =2) %>%
  kable_minimal()
```

Logging helps and substitution not as strong:

```{r}
lm_robust(log(cash_billions+1) ~ trading_factor*risk_factor+ round, fixed_effects = ~id,  se_type = "stata", data = df_4) %>% tidy  %>% 
  kbl(digit =2) %>%
  kable_minimal()

```

## Full results from saturated models

```{r}
main_results %>% 
  kbl(digit =2) %>%
  kable_minimal()
```


# Table 2: Structural Analysis

We assume:

$$ u =  (a + bT + cR)  \log(Y + x) - x^2 - g(x - ky)^2$$

where $T$ is trading importance, $R$ is health risk, $Y$ is total Amount given by other countries and $y$ is average Amount given by other countries

First order condition for maximization is:

$$\frac{(a + bT + cR)}{ (Y + x)} - 2x - 2g(x - ky) = 0$$
This yields the following quadratic. We take the second solution (with positive contributions).

$$- 2(1+g)x^2- 2((1+g)Y - gky)x +(2gkyY+(a + bT + cR)) = 0$$

```{r}
# Quadratic solution
maxx <- function(a,b,c,g,k,ZT,ZR,ZY,Zy) {
  AA = -2*(1+g)
  BB = -2*((1+g)*ZY - g*k*Zy)
  CC = 2*g*k*Zy*ZY + a+b*ZT+c*ZR
  (-BB - (BB^2 - 4*AA*CC)^.5)/(2*AA)
}
maxx(a=1,b=1,c=1,g=1, k=1,ZT=1,ZR=1,ZY=1,Zy=1)

```


```{r}

lik_x <- function(x, sigma, a,b,c,g,k,ZT,ZR,ZY,Zy) 
      dnorm(x, 
            maxx(a, b, c, g, k, ZT, ZR, ZY, Zy), 
            sd = sigma)

# Estimation

est <- function(data){

  LL  <- function(a=1,b=1,c=1,g=1,k=1, sigma=1) {
    
    R <- with(data, 
          lik_x(x, 
             sigma, 
             a, b, c, g, k,
             ZT = trading_importance,
             ZR = risk,
             ZY = others_giving,
             Zy = others_average))

    -sum(log(R))
  }


  M <- bbmle::mle2(
    LL,
    # method = "L-BFGS-B",
    optimizer = "nlminb",
    start = list(a = 1, b = 1, c = 1, g = 2,  k = 1, sigma = .05),
    lower = list(a = -20, b = -10, c = -20, g = .01, k = -10, sigma = .02),
    upper = list(a = 20, b = 10, c = 10, g = 10, k = 10, sigma = 10))
  
  # Format output from estimation
  out <- bbmle::coef(bbmle::summary(M)) %>% data.frame()
  
  names(out) <- c("estimate", "std.error", "statistic", "p.value")
  
  out %>% mutate(conf.low = estimate - 1.96*std.error, 
                 conf.high = estimate + 1.96*std.error)

}

```


Note structural estimates do not include fixed effects.

```{r}

# Note that starting values were found using  a grid search to approximate the region of the solution

df_4 <- df_4 %>% mutate(x = cash_billions)

  LL  <- function(a=1,b=1,c=1,g=1,k=1, sigma=1) {
    
    R <- with(df_4, 
          lik_x(x, 
             sigma, 
             a, b, c, g, k,
             ZT = trading_importance,
             ZR = risk,
             ZY = others_giving,
             Zy = others_average))

    -sum(log(R))
  }
  
# .a    .b    .c    .g    .k  .sigma
# 243.   -10  36.7 0.667     5     16
  
M <- bbmle::mle2(
    LL,
    # method = "L-BFGS-B",
    optimizer = "nlminb",
    start = list(a = 240, b = -11, c = 41, g = .8,  k = 4, sigma = 16),
    lower = list(a = 0, b = -20, c = -60, g = .01, k = -10, sigma = .02),
    upper = list(a = 400, b = 20, c = 60, g = 5, k = 10, sigma = 30))
  
  # Format output from estimation
  out <- bbmle::coef(bbmle::summary(M)) %>% data.frame()
  
  names(out) <- c("estimate", "std.error", "statistic", "p.value")
  
  # Flag: Should be able to do better ci's than this
  out %>% mutate(conf.low = estimate - 1.96*std.error, 
                 conf.high = estimate + 1.96*std.error) %>% kable(format = "pipe", digits = 2)


fileConn <- file("2_output/structural.tex")
writeLines(
  out %>% mutate(parameter = c("$\\alpha$", "$\\beta$", "$\\delta$", "$\\gamma$", "$\\kappa$", "$\\sigma$")) %>%
    relocate(parameter) %>%
    mutate(conf.low = estimate - 1.96*std.error, 
                 conf.high = estimate + 1.96*std.error) %>%
    
    kable(format = "latex", 
          caption = "Structural parameter estimates",
          digits = 2, 
          booktabs = TRUE, 
          label = "structural", row.names = FALSE,
          escape = FALSE, 
          align = c("c", "r", "r", "r", "r", "r", "r")) %>%
    kable_styling(latex_options = "hold_position"), 
  
  fileConn)

close(fileConn)



```


<!-- Note that, without fixed effects, trading importance is also weakly negative in the design based analysis: -->

```{r, include = FALSE, echo = FALSE}
lm_robust(cash_billions ~ trading_importance*risk*others_number_norm*others_giving_norm  + round,  se_type = "stata", data = df_4) %>% tidy %>% kable(digits = 2)
```

```{r, include = FALSE, eval = FALSE}
## Manual ML to find starting values
maxp = 3
lp = 7
pars <- expand_grid(
  .a = seq(210, 310, length = lp),
  .b = seq(-15, -5, length = lp),
  .c = seq(30, 50, length = lp),
  .g = seq(0, 4, length = lp),
  .k = seq(1, 5, length = lp),
  .sigma = seq(12, 20, length = lp)) 

Ls <- sapply(1:nrow(pars), function(j) pars %>% slice(j) %>%
  mutate(L = LL(a=.a, b=.b, c=.c, g=.g, k=.k, sigma=.sigma)) %>% 
    pull(L))

Ls[is.nan(Ls)] <- Inf

pars %>% dplyr::filter(Ls == min(Ls))
```




# Figure 3: Effect of video treatment on individual solidarity

```{r}
outcomes <- c("solidarity_behaviour", "solidarity_attitude")
outcome_labels <- c("Solidarity Behavior", "Solidarity Attitude")
w2_treatments <- c("treatment_video")
w2_treatment_labels <- c("Treatment")
```

```{r, results = "asis"}

df_2 %>% group_by(treatment_video, solidarity_behaviour) |>
  summarize(n = n()) |>
  filter(!is.na(solidarity_behaviour)) |>
  ungroup() |>
  group_by(treatment_video) |>
  mutate(share = n / sum(n)) |>
  kable(caption = "Raw data", format = "pipe")

#    keep           donate UNICEF
#1  0 Mingle Points 75 Mingle Points
#2 10 Mingle Points 60 Mingle Punkte
#3 20 Mingle Points 45 Mingle Points
#4 30 Mingle Points 30 Mingle Points
#5 40 Mingle Points 15 Mingle Points
#6 50 Mingle Points 0 Mingle Points

hist1<-df_2 %>%
  ggplot( aes(x = solidarity_behaviour)) + 
  geom_histogram()+
  theme_bw() + facet_grid(~treatment_video)


hist2<-df_2 %>%
  ggplot( aes(x = solidarity_attitude)) + 
  geom_histogram()+
  theme_bw()  + facet_grid(~treatment_video)

hist1
hist2

models_basic <- lapply(c(outcomes), function(y)
lm_robust(as.formula(paste(y, "~ treatment_video")), 
          data = df_2))
names(models_basic) <- outcomes


figure_3 <- 
  lapply(models_basic, tidy) %>% bind_rows(.id = "outcome") %>%
  dplyr::filter(term != "(Intercept)") %>%
  mutate(outcome = factor(outcome, outcomes, outcome_labels)) %>%
  ggplot(aes(estimate, outcome)) + geom_point()+
  geom_errorbar(aes(xmin = conf.low, xmax = conf.high), width = .1)+
  geom_vline(xintercept=0, linetype="longdash", lwd=0.35, colour = "#B55555") + 
  theme_bw() +
  #ggtitle("Effect of video treatment") +
  ylab("")



figure_3

pdf("2_output/figure_3.pdf", width = 6, height = 3)
figure_3


models_basic %>% lapply(tidy) |> bind_rows() |> 
  kable(captin = "lm_robust estimates", format = "pipe")
 
```





# Figure 6: Levels of support by party

```{r}

sp <- lapply(unique(df_4$party), function(p)
support(
    df_4 %>% dplyr::filter(party == p) %>% pull(cash_billions), 
    amounts = amounts_d))
names(sp) <- unique(df_4$party)

sp <- sp %>% bind_rows(.id = "Party")

supports_by_party <- 
  sp %>% ggplot(aes(amounts, support, color = Party)) + geom_line() + ylim(0,1) + theme_bw() + xlab("German contribution (bn Euro)") + ylab("Share supporting")  + theme(legend.position="bottom")

pdf("2_output/cumulative_by_party.pdf", height = 6, width = 10)
 supports_by_party 
dev.off()

supports_by_party

```

# Figure 7: Levels of support by migration background

```{r}

sm <- lapply(0:1, function(m)
  support(
    df_4 %>% dplyr::filter(migration_background == m) %>% pull(cash_billions), 
    amounts = amounts_d))
names(sm) <- c("Non migrant", "Migrant")

sm <- sm %>% bind_rows(.id = "Migration_background")

supports_by_migration <- 
  sm %>% ggplot(aes(amounts, support, color = Migration_background)) + geom_line() + ylim(0,1) + theme_bw() + xlab("German contribution (bn Euro)") + ylab("Share supporting")  + theme(legend.position="bottom")

pdf("2_output/cumulative_by_migration.pdf", height = 6, width = 10)
 supports_by_migration 
dev.off()

supports_by_migration

```


# Figure 8: Marginal effects of conditions by party

```{r}
main_results_by_party <- 
  lapply(unique(df_4$party), function(p)
    list(
      cash = lm_robust(cash_billions ~ trading_importance*risk*others_number_norm*others_giving_norm  + round,
                       fixed_effects = ~id,  se_type = "stata", 
                       data = df_4 %>% dplyr::filter(party == p)) %>% tidy,
      doses = lm_robust(doses ~ trading_importance*risk*others_number_norm*others_giving_norm  + round,
                        fixed_effects = ~id,  se_type = "stata", 
                        data = df_4 %>% dplyr::filter(party == p)) %>% tidy) %>% 
      bind_rows() %>% mutate(party = p)) %>%   
  bind_rows()

figure_1_party <-
  
  main_results_by_party %>% 
  dplyr::filter(term %in% treatments_norm) %>% 
  mutate(Treatment = factor(term, treatments_norm, treatment_labels),
         outcome = factor(outcome, c("cash_billions", "doses"), c("Cash (billion Euros)", "Doses (Millions)"))) %>%
  
  ggplot(aes(Treatment, estimate, color = party)) + 
  geom_point(position = position_dodge(0.3))+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), position = position_dodge(0.3), width = .1)+
  geom_hline(yintercept=0, linetype="longdash", lwd=0.35, colour = "#B55555") + 
  theme_bw() + facet_grid(~outcome, scales = "free_x")+
  xlab("") +
  coord_flip()

figure_1_party

pdf("2_output/figure_1_party.pdf", width = 9, height = 7)
 figure_1_party
dev.off()

```

# Figure 9: Marginal effects of conditions by migration background

```{r}
main_results_by_background <- 
  lapply(unique(df_4$migration_background), function(p)
    list(
      cash = lm_robust(cash_billions ~ trading_importance*risk*others_number_norm*others_giving_norm  + round,
                       fixed_effects = ~id,  se_type = "stata", 
                       data = df_4 %>% dplyr::filter(migration_background == p)) %>% tidy,
      doses = lm_robust(doses ~ trading_importance*risk*others_number_norm*others_giving_norm  + round,
                        fixed_effects = ~id,  se_type = "stata", 
                        data = df_4 %>% dplyr::filter(migration_background == p)) %>% tidy) %>% 
      bind_rows() %>% mutate(migration_background = factor(p))) %>%   
  bind_rows()

figure_1_background <-
  
  main_results_by_background %>% 
  dplyr::filter(term %in% treatments_norm) %>% 
  mutate(Treatment = factor(term, treatments_norm, treatment_labels),
         outcome = factor(outcome, c("cash_billions", "doses"), c("Cash (billion Euros)", "Doses (Millions)"))) %>%
  
  ggplot(aes(Treatment, estimate, color = migration_background)) + 
  geom_point(position = position_dodge(0.3))+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), position = position_dodge(0.3), width = .1)+
  geom_hline(yintercept=0, linetype="longdash", lwd=0.35, colour = "#B55555") + 
  theme_bw() + facet_grid(~outcome, scales = "free_x")+
  xlab("") +
  coord_flip()

figure_1_background

pdf("2_output/figure_1_background.pdf", width = 9, height = 4)
 figure_1_background
dev.off()

```


# Figure 10: Results Refreshment Sample

```{r}

# 5.2 Main results by group
main_results_by_group <- 
  lapply(unique(df_4$group), function(p)
    list(
      cash = lm_robust(cash_billions ~ trading_importance*risk*others_number_norm*others_giving_norm  + round,
                       fixed_effects = ~id,  se_type = "stata", 
                       data = df_4 %>% dplyr::filter(group == p)) %>% tidy,
      doses = lm_robust(doses ~ trading_importance*risk*others_number_norm*others_giving_norm  + round,
                        fixed_effects = ~id,  se_type = "stata", 
                        data = df_4 %>% dplyr::filter(group == p)) %>% tidy) %>% 
      bind_rows() %>% mutate(group = factor(p))) %>%   
  bind_rows()

figure_1_group <-
  
  main_results_by_group %>% 
  dplyr::filter(term %in% treatments_norm) %>% 
  mutate(Treatment = factor(term, treatments_norm, treatment_labels),
         outcome = factor(outcome, c("cash_billions", "doses"), c("Cash (billion Euros)", "Doses (Millions)"))) %>%
  ggplot(aes(Treatment, estimate, group=group, color = group)) + 
  geom_point(position = position_dodge(0.3))+
  scale_color_discrete(name = "Sample", labels = c("refreshment", "main"))+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), position = position_dodge(0.3), width = .1)+
  geom_hline(yintercept=0, linetype="longdash", lwd=0.35, colour = "#B55555") + 
  theme_bw() + facet_grid(~outcome, scales = "free_x")+
  xlab("") +
  coord_flip() 

figure_1_group
pdf("2_output/figure_1_group.pdf", width = 9, height = 4)
figure_1_group
dev.off()


```










# Additional Analyses

## Individual solidarity

Should an older Indian woman be prioritized over a young German?

```{r}


## Prioritization analysis

df_4 <- df_4 %>% mutate( 
    de_de_preference  = perspective_fed_german - perspective_fed_indian # DE Preference for German 25
)

df_4 %>% 
  summarize(
    priority_de_indian = mean(perspective_fed_indian),
    priority_de_german = mean(perspective_fed_german),
 #   priority_who_indian = mean(perspective_who_indian),
#    priority_who_german = mean(perspective_who_german),
    de_ind_preference  = mean(perspective_fed_german <= perspective_fed_indian),
    de_ind_preference2  = mean(perspective_fed_german < perspective_fed_indian),
    de_ind_preference3  = mean(perspective_fed_german == perspective_fed_indian),
 #   who = mean(who_de_preference, na.rm = TRUE),
 #   who_priority = mean(who_de_preference>0, na.rm = TRUE)
    ) %>% t %>% kable(format = "pipe")
```

About 57% of Germans think that a German 25 year old should be at least as high a priority as an Indian 65 year old. 22% think the same for WHO priortization.

```{r}
M <- 
  lm_robust(cash_billions_log ~  perspective_fed_german + perspective_fed_indian, data = df_4)
M %>% tidy %>% kable(digits = 2)

# M$r.squared
# plot(df_4$cash_billions_log, df_4$perspective_fed_indian)


```

```{r}

hist(df_4$perspective_fed_german - df_4$perspective_fed_indian,
     main = "difference in support for federal action for  german and indian")

lm_robust(log(cash_billions+1) ~ trading_factor*risk_factor+ treatment_video + round + perspective_fed_german +perspective_fed_indian,  se_type = "stata", data = df_4) %>% tidy  %>% 
  kbl(digit =2) %>%
  kable_minimal()

```



```{r}
raw  <- 
  df_4 %>% 
  mutate(costs = ((risk_factor == "High") + 2*(trading_factor=="High"))) %>%
  group_by(trading_factor, risk, deal, costs) %>% 
  summarize(cash_bn = median(cash_billions, na.rm = TRUE),
            doses = median(doses, na.rm = TRUE))  %>%
  gather("outcome","value",  -risk,  -deal, -trading_factor, -costs)

medians_plot <- 
raw %>% ggplot(aes(risk, value, color = trading_factor)) + 
  facet_grid(outcome ~ deal, scales = "free_y") + geom_point()  + geom_line() + ylim(c(0, NA)) + theme_bw() + ylab(" ")+
  scale_x_continuous(breaks=c(-.45,.45), labels = c("Low", "High")) 

pdf("2_output/medians.pdf", height = 5, width = 8)
 medians_plot 
dev.off()
# Note: use bootstrapping to add standard errors on the median?



observation_plot <- function(data = df_4)
data %>% dplyr::select(risk_factor, deal, trading_factor, cash_billions, doses, vaccinated) %>%
  mutate(cash_billions = ifelse(cash_billions>20, 20, cash_billions)) %>%
  gather("outcome","value",  -risk_factor,  -deal, -trading_factor, - vaccinated) %>%
  mutate(outcome = factor(outcome, c("cash_billions", "doses"), c("Billion Euros", "Million doses"))) %>% 
  ggplot(aes(risk_factor, value, color = trading_factor)) + facet_grid(outcome ~ deal, scales = "free_y") + 
  geom_boxplot() + ylim(c(0, NA)) + theme_bw() + 
  scale_y_continuous(trans='sqrt') + 
  ylab(" ") + xlab("Mutation risk") 


observation_plot
```

##  Wave 2 conjoint

A conjoint was also implemented in Wave 2 but with a flawed design. The wave 2 values were poorly calibrated and question wording left ambiguity regarding beneficiaries as  the benefits conditions are conceptually confused  with numbers conditions.

Analysis is implemented and reported here in the interests of completeness.

```{r, results = "asis"}

label <- "1_input/W2_exp3_vignettes_universe.dta" %>% 
  read_dta() %>%  
    mutate(vignr = as.numeric(vignr))


# label |>  head() |> kable(caption = "W2 vignettes")


conjoints <- 
  
  list(
    conjoint1_1 =
      df_2 %>%
      mutate(vignr = as.numeric(c_0031_w2),
             outcome = conjoint_choice1_exp3, 
             rating = conjoint_rating1_exp3, 
             contest = 1, candidate=1), 
    
  conjoint1_2 =
      df_2 %>%
      mutate(vignr = as.numeric(c_0032_w2),
             outcome = conjoint_choice1_exp3, 
             rating = conjoint_rating2_exp3, 
             contest = 1, candidate=2),
    
  conjoint2_1 =
      df_2 %>%
      mutate(vignr = as.numeric(vignette3),
             outcome = conjoint_choice2_exp3, 
             rating = conjoint_rating3_exp3, 
             contest = 2, candidate=1),
        
    conjoint2_2 =
      df_2 %>%
      mutate(vignr = as.numeric(vignette4),
             outcome = conjoint_choice2_exp3, 
             rating = conjoint_rating4_exp3, 
             contest = 2, candidate=2),
  
  conjoint3_1 =
      df_2 %>%
      mutate(vignr = as.numeric(vignette5),
             outcome = conjoint_choice3_exp3, 
             rating = conjoint_rating5_exp3, 
             contest = 3, candidate=1),
  
  conjoint3_2 =
      df_2 %>%
      mutate(vignr = as.numeric(vignette6),
             outcome = conjoint_choice3_exp3, 
             rating = conjoint_rating6_exp3, 
             contest = 3, candidate=2)  
                    
) %>% 
  bind_rows() %>%
  select(ID, vignr, outcome, rating, contest, candidate, treatment_video) %>%
  mutate(
    outcome = ifelse(candidate ==1, 
                     as.numeric(outcome=="1"),
                     as.numeric(outcome=="2"))) %>%
  left_join(label) %>%
  mutate(
    doses = factor(
      vig_doses, 0:3,
      c("1 Million doses", "5 Million doses", "10 Million doses", "20 Million doses")),
    share = factor(vig_dose_share, 0:3,
      c("1 % of the vaccines", "5 % of the vaccines", "10 % of the vaccines", "20 % of the vaccines")),
    number= factor(vig_countries, 0:2, c("20 countries", "80 countries", "160 countries")), 
    economic_benefits= factor(vig_benefit_economic, 0:1, c("Without economic importance", "With economic importance")),
    health_benefits=factor(vig_benefit_health, 0:1,  
      c("No risk of infection", "Risk of infection"))) 

# Demean data
# Note that mean rating is removed
conjoints_norm <- conjoints %>% 
  mutate(doses_norm = vig_doses - mean(vig_doses),
         number_norm = vig_countries - mean(vig_countries),
         share_norm = vig_dose_share - mean(vig_dose_share),
         economic_benefits = vig_benefit_economic - mean(vig_benefit_economic),
         health_benefits = vig_benefit_health - mean(vig_benefit_health)) %>%
  group_by(ID) %>% 
  mutate(rating = rating - mean(rating)) %>% ungroup 


models_interactions <-
  list(
    rating0 = lm_robust(rating ~  doses_norm*share_norm*number_norm*economic_benefits*health_benefits, data = conjoints_norm),
    rating1 = lm_robust(rating ~  doses_norm*share_norm*number_norm*economic_benefits*health_benefits, data = conjoints_norm),
    choice0 = lm_robust(outcome ~  doses_norm*share_norm*number_norm*economic_benefits*health_benefits, data = conjoints_norm),
    choice1 = lm_robust(outcome ~  doses_norm*share_norm*number_norm*economic_benefits*health_benefits, data = conjoints_norm)
  )


models_treatments <-
  list(
    rating = lm_robust(rating ~  treatment_video*vig_doses + treatment_video*vig_dose_share + treatment_video*vig_countries + treatment_video*vig_benefit_economic + treatment_video*vig_benefit_health, 
                        data = conjoints_norm),
    choice = lm_robust(outcome ~  treatment_video*vig_doses + treatment_video*vig_dose_share + treatment_video*vig_countries + treatment_video*vig_benefit_economic + treatment_video*vig_benefit_health, 
                        data = conjoints_norm)
    )

htmlreg(models_interactions)

htmlreg(models_treatments)

fileConn <- file("2_output/treatment_effects.tex")
writeLines(texreg(models_treatments, float.pos = "h!", include.ci = FALSE, caption = "Effects of treatment on drivers of support for agreements. ",
  custom.coef.map = list(
    "(Intercept)" = "Constant (Average rating)",
    "treatment_video" = "Video effect (given ungenerous agreement)",
    "vig_doses" = "German contribution",
    "vig_dose_share" = "German share",
"vig_countries" = "Number of donors",
"vig_benefit_economic" = "Economic benefits",
"vig_benefit_health" = "Health benefits",
"treatment_video:vig_doses" = "Video * Contribution",
"treatment_video:vig_dose_share" = "Video * Share",
"treatment_video:vig_countries" = "Video * Donors",
"treatment_video:vig_benefit_economic" = "Video * Economics",
"treatment_video:vig_benefit_health"= "Video * Health"
    ), digits = 3), fileConn)
close(fileConn)


      
```




```{r}
# Save workspace
save.image("Solidarity.Rdata")
```


